Learning constraints in tabular data

### 2016-05-24 Paper/ECAI/tabular.tex
Small edits table

\caption{Overview of constraint templates implemented in our system, which covers the most popular spreadsheet constraints we encountered. The templates marked with $\dagger$ are aggregate constraint templates, the table shows the version for sum but the implementation also supports max, min, average, product and count. Subgroups in normal font have to be vectors, while subgroups in \textbf{bold} may contain more than one vector.\label{table:constraints}}

@@

    $\ecalldiff{\sg_x}$

@@

    $\ecperm{\sg_x}$

@@

    \ecfkey{\sg_{fk}}{\sg_{pk}} & $\sg_{fk}$ and~$\sg_{pk}$ are both $\discrete$; $\ptype(\sg_{fk}) = \ptype(\sg_{pk})$; $\ptable(\sg_{fk}) \neq \ptable(\sg_{pk})$; and $\ecalldiff{\sg_{pk}}$ & Every value in~$\sg_{fk}$ also exist in~$\sg_{pk}$ \\ \hline

>>>>

\caption{Overview of constraint templates implemented in \sname.
The templates marked with $\dagger$ are aggregate constraint templates, the table shows the version for sum but the implementation also supports max, min, average, product and count.
Subgroups in normal font have to be vectors, while subgroups in \textbf{bold} may contain more than one vector.
Templates marked with $*$ are \textit{structural}, i.e. they are not functional and cannot be implemented in most spreadsheet software.}\label{table:constraints}

@@

    $\ecalldiff{\sg_x}^*$

@@

    $\ecperm{\sg_x}^*$

@@

    $\ecfkey{\sg_{fk}}{\sg_{pk}}^*$ & $\sg_{fk}$ and~$\sg_{pk}$ are both $\discrete$; $\ptype(\sg_{fk}) = \ptype(\sg_{pk})$; $\ptable(\sg_{fk}) \neq \ptable(\sg_{pk})$; and $\ecalldiff{\sg_{pk}}$ & Every value in~$\sg_{fk}$ also exist in~$\sg_{pk}$ \\ \hline
